Gammapy: A Python package for gamma-ray astronomy

### 2023-03-22 src/ms-review.tex

%% \gammaray astronomy
%% CN: I think we should use the expression Water Cherenkov Detectors and use the
%% abbreviation (WCD) all along the text, later we use "particle samplers"
The \gammaray range of the electromagnetic spectrum provides us insights into the
most energetic processes in the universe such as those accelerating particles in the surroundings of
black holes, and remnants of supernova explosions. As in other
branches of astronomy, \gammarays can be observed by
satellite as well as ground-based instruments.
Ground-based instruments use the Earth's atmosphere as a particle detector.
Very-high-energy (VHE) cosmic \gammarays interact in the atmosphere and
create large showers of secondary particles that can be observed from the ground.
Ground-based \gammaray astronomy relies on these extensive air showers to detect the
primary \gammaray photons and infer their incident direction and energy.
VHE \gammaray astronomy covers the energy range from few tens of \si{GeV} up to the \si{PeV}.
There are two main categories of ground-based instruments:

>>>>

%% \gammaray astronomy
In modern astronomy astrophysical objects are studied across
all wavelengths. The \gammaray range of the electromagnetic spectrum 
provides us insights into the most energetic processes in the universe such as
those accelerating particles in the surroundings of black holes or remnants of
supernova explosions.

In general \gammaray astronomy relies on the detection of individual 
photon events and reconstruction of their incident direction as well
as energy. As in other branches of astronomy, this can be
achieved by satellite as well as ground-based \gammaray instruments.
Space based instruments such as the Fermi Large Area Telescope (LAT)
rely on the pair-conversion effect to detect \gammarays and track
the positron-electron pairs created in the detector to reconstruct the incident direction 
of the incoming \gammaray. The energy of the photon is estimated using a calorimeter
at the bottom of the instrument. The energy range of \fermi ranges from
\SI{20}{MeV} to \SI{300}{GeV}.

Ground-based instruments use the Earth's atmosphere as a particle detector instead.
Very-high-energy (VHE) cosmic \gammarays interact in the atmosphere and
create large showers of secondary particles that can be observed from the ground.
Ground-based \gammaray astronomy relies on these extensive air showers to detect the
primary \gammaray photons and infer their incident direction and energy.
VHE \gammaray astronomy covers the energy range from few tens of \si{GeV} up to the \si{PeV}.
There are two main categories of ground-based instruments:
